Approximation as Differentiation notes

### 2025-02-10 notes.tex
The two semilattice structures share a partial order.
Ignoring lists for now.

Define the category $\LatGal$ where:
\begin{itemize}
\item objects $L$ are bounded lattices;
\item morphisms $(f, g)$ from $L$ to $L'$ are meet-semilattice homomorphisms $f: L \to L'$ paired with
join-semilattice homomorphisms $g: L' \to L$ satisfying $y \leq fx \iff gy \leq x$.
\end{itemize}

\noindent \note{The Agda defines an object of $\LatGal$ as a set equipped with meet- and join-semilattice
structures but there is no requirement that they satisfy the absorption laws or induce the same partial
order.}

>>>>

Define the category $\LatGal$ where:
\begin{itemize}
\item objects $L$ are the bounded lattices;
\item morphisms $f \vdash g: L \to L'$ are meet-semilattice homomorphisms $f: L \to L'$ paired with
join-semilattice homomorphisms $g: L' \to L$ satisfying $y \leq fx \iff gy \leq x$ for any $x \in L$ and any
$y \in L'$.
\end{itemize}

\noindent $\LatGal$ has finite biproducts. \todo{Tie this to pre-additive structure.}

\subsection{Semantic domain}

We interpret our language into any category with:
\begin{itemize}
\item finite products (binary products and a terminal object)
\end{itemize}
\note{Ignoring lists for now.}
